{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-19 paper/tex/paper.tex
floor feedback: discussion (part II) + comparisons
add long awaited extended mission results
add description of lower mass gap plot
BIG COMMIT: lots of changes from Selma
change software citations

\newcommand{\BHBHFourYear}{74}
\newcommand{\BHNSFourYear}{42}
\newcommand{\NSNSFourYear}{8}
\newcommand{\BHBHTenYear}{TODO}
\newcommand{\BHNSTenYear}{TODO}
\newcommand{\NSNSTenYear}{TODO}

% number of systems that are definitely not WDWDs
\newcommand{\BHBHNotWDWDFour}{33}
\newcommand{\BHNSNotWDWDFour}{16}
\newcommand{\NSNSNotWDWDFour}{5}
\newcommand{\BHBHNotWDWDTen}{TODO}
\newcommand{\BHNSNotWDWDTen}{TODO}
\newcommand{\NSNSNotWDWDTen}{TODO}

% percentage of systems above Chandrasekhar mass
\newcommand{\BHBHAboveMaxWDWDFourPerc}{17}
\newcommand{\BHNSAboveMaxWDWDFourPerc}{21}
\newcommand{\NSNSAboveMaxWDWDFourPerc}{3}
\newcommand{\BHBHAboveMaxWDWDTenPerc}{TODO}
\newcommand{\BHNSAboveMaxWDWDTenPerc}{TODO}
\newcommand{\NSNSAboveMaxWDWDTenPerc}{TODO}

% number of systems that can be determined as either a BH or NS
\newcommand{\BHBHEitherBHOrNSFour}{11}
\newcommand{\BHNSEitherBHOrNSFour}{6}
\newcommand{\NSNSEitherBHOrNSFour}{3}
\newcommand{\BHBHEitherBHOrNSTen}{TODO}
\newcommand{\BHNSEitherBHOrNSTen}{TODO}
\newcommand{\NSNSEitherBHOrNSTen}{TODO}
\newcommand{\BHBHEitherBHOrNSFourPerc}{14}
\newcommand{\BHNSEitherBHOrNSFourPerc}{13}
\newcommand{\NSNSEitherBHOrNSFourPerc}{35}
\newcommand{\BHBHEitherBHOrNSTenPerc}{TODO}
\newcommand{\BHNSEitherBHOrNSTenPerc}{TODO}
\newcommand{\NSNSEitherBHOrNSTenPerc}{TODO}

% percentage of systems in lower mass gap
\newcommand{\BHBHLowerMassGap}{35\%}
\newcommand{\BHNSLowerMassGap}{38\%}

@@

% percentage of systems with e > 0.01
\newcommand{\BHBHNotCirc}{86\%}
\newcommand{\BHNSNotCirc}{47\%}
\newcommand{\NSNSNotCirc}{86\%}

% percentage of systems with e > 0.3
\newcommand{\BHBHHighlyEccentric}{22\%}
\newcommand{\BHNSHighlyEccentric}{8\%}
\newcommand{\NSNSHighlyEccentric}{12\%}

% percentage of systems with something other than 1 detectable harmonic
\newcommand{\BHBHMultipleHarmonicsFourPerc}{55}
\newcommand{\BHNSMultipleHarmonicsFourPerc}{28}
\newcommand{\NSNSMultipleHarmonicsFourPerc}{66}
\newcommand{\BHBHMultipleHarmonicsTenPerc}{TODO}
\newcommand{\BHNSMultipleHarmonicsTenPerc}{TODO}
\newcommand{\NSNSMultipleHarmonicsTenPerc}{TODO}

% percentage of systems with >1 harmonic and in disc
\newcommand{\BHBHEccInDiscFourPerc}{40}
\newcommand{\BHNSEccInDiscFourPerc}{25}
\newcommand{\NSNSEccInDiscFourPerc}{60}
\newcommand{\BHBHEccInDiscTenPerc}{TODO}
\newcommand{\BHNSEccInDiscTenPerc}{TODO}
\newcommand{\NSNSEccInDiscTenPerc}{TODO}

% percentage of systems with fractional chirp mass uncertainty < 1
\newcommand{\BHBHChirpMassMeasureable}{20}
\newcommand{\BHNSChirpMassMeasureable}{17}
\newcommand{\NSNSChirpMassMeasureable}{4}

@@

\section{Results I - Fiducial} \label{sec:results}
\input{sections/results.tex}

\section{Results II - Model variations} \label{sec:variations}
\input{sections/variations.tex}

@@

\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios, it is freely available at \url{https://legwork.readthedocs.io/en/latest/}. Simulations in this paper made use of the COMPAS rapid binary population synthesis code, which is freely available at \url{http://github.com/TeamCOMPAS/COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}. The simulations performed in this work were simulated with a COMPAS version that predates the publicly available code. Our version of the code is most similar to version 02.13.01 of the publicly available COMPAS code. Requests for the original code can be made to Floor Broekgaarden. The authors used {\sc{STROOPWAFEL}} from \citep{Broekgaarden+2019}, publicly available at \url{https://github.com/FloorBroekgaarden/STROOPWAFEL}\footnote{For the latest pip installable version of STROOPWAFEL please contact Floor Broekgaarden.}.
The authors also made use of Python from the Python Software Foundation. Python Language Reference, version 3.6. Available at \url{http://www.python.org}. In addition the following Python packages were used: matplotlib \citep{Hunter+2007},  {NumPy} \citep{vanderWalt+2011}, SciPy \citep{Virtanen+2020}, Jupyter Lab \citep{Kluyver+2016}, seaborn \citep{Waskom+2020}, h5py \citep{Collette+2021} and Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.  This research has made use of NASA’s Astrophysics Data System Bibliographic Services. We also made use of the computational facilities from the Harvard FAS Research Computing cluster.}

>>>>

\newcommand{\BHBHFourYear}{74}
\newcommand{\BHNSFourYear}{42}
\newcommand{\NSNSFourYear}{8}
\newcommand{\BHBHTenYear}{118}
\newcommand{\BHNSTenYear}{71}
\newcommand{\NSNSTenYear}{13}

% percentage of systems in lower mass gap
\newcommand{\BHBHLowerMassGap}{35\%}
\newcommand{\BHNSLowerMassGap}{39\%}

@@

% percentage of systems with e > 0.01
\newcommand{\BHBHNotCirc}{87\%}
\newcommand{\BHNSNotCirc}{46\%}
\newcommand{\NSNSNotCirc}{86\%}

% percentage of systems with e > 0.3
\newcommand{\BHBHHighlyEccentric}{21\%}
\newcommand{\BHNSHighlyEccentric}{8\%}
\newcommand{\NSNSHighlyEccentric}{12\%}

% number of systems with fractional chirp mass uncertainty < 1
\newcommand{\BHBHChirpMassMeasureableFour}{20}
\newcommand{\BHNSChirpMassMeasureableFour}{17}
\newcommand{\NSNSChirpMassMeasureableFour}{4}
\newcommand{\BHBHChirpMassMeasureableTen}{52}
\newcommand{\BHNSChirpMassMeasureableTen}{44}
\newcommand{\NSNSChirpMassMeasureableTen}{9}

% percentage of systems above Chandrasekhar mass
\newcommand{\BHBHAboveMaxWDWDFourPerc}{24}
\newcommand{\BHNSAboveMaxWDWDFourPerc}{28}
\newcommand{\NSNSAboveMaxWDWDFourPerc}{4}
\newcommand{\BHBHAboveMaxWDWDTenPerc}{38}
\newcommand{\BHNSAboveMaxWDWDTenPerc}{41}
\newcommand{\NSNSAboveMaxWDWDTenPerc}{5}

% percentage of systems with something other than 1 detectable harmonic
\newcommand{\BHBHMultipleHarmonicsFourPerc}{55}
\newcommand{\BHNSMultipleHarmonicsFourPerc}{27}
\newcommand{\NSNSMultipleHarmonicsFourPerc}{66}
\newcommand{\BHBHMultipleHarmonicsTenPerc}{61}
\newcommand{\BHNSMultipleHarmonicsTenPerc}{29}
\newcommand{\NSNSMultipleHarmonicsTenPerc}{68}

% percentage of systems with >1 harmonic and in disc
\newcommand{\BHBHEccInDiscFourPerc}{40}
\newcommand{\BHNSEccInDiscFourPerc}{23}
\newcommand{\NSNSEccInDiscFourPerc}{59}
\newcommand{\BHBHEccInDiscTenPerc}{40}
\newcommand{\BHNSEccInDiscTenPerc}{23}
\newcommand{\NSNSEccInDiscTenPerc}{59}

% number of systems that are definitely not WDWDs
\newcommand{\BHBHNotWDWDFour}{37}
\newcommand{\BHNSNotWDWDFour}{18}
\newcommand{\NSNSNotWDWDFour}{5}
\newcommand{\BHBHNotWDWDTen}{70}
\newcommand{\BHNSNotWDWDTen}{38}
\newcommand{\NSNSNotWDWDTen}{8}

% number of systems that can be determined as either a BH or NS
\newcommand{\BHBHEitherBHOrNSFour}{16}
\newcommand{\BHNSEitherBHOrNSFour}{7}
\newcommand{\NSNSEitherBHOrNSFour}{4}
\newcommand{\BHBHEitherBHOrNSTen}{39}
\newcommand{\BHNSEitherBHOrNSTen}{17}
\newcommand{\NSNSEitherBHOrNSTen}{8}
\newcommand{\BHBHEitherBHOrNSFourPerc}{21}
\newcommand{\BHNSEitherBHOrNSFourPerc}{18}
\newcommand{\NSNSEitherBHOrNSFourPerc}{47}
\newcommand{\BHBHEitherBHOrNSTenPerc}{33}
\newcommand{\BHNSEitherBHOrNSTenPerc}{24}
\newcommand{\NSNSEitherBHOrNSTenPerc}{62}

\newcommand{\BHBHatLeastOneLowerMassGapPerc}{69}
\newcommand{\BHNSatLeastOneLowerMassGapPerc}{39}
\newcommand{\NSNSatLeastOneLowerMassGapPerc}{0}
\newcommand{\ALLatLeastOneLowerMassGapPerc}{55}

@@

\section{Results I - Predictions for LISA sources} \label{sec:results}
\input{sections/results.tex}

\section{Results II - Impact of physics assumptions} \label{sec:variations}
\input{sections/variations.tex}

@@

\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios, it is freely available at \url{https://legwork.readthedocs.io/en/latest/}. Simulations in this paper made use of the COMPAS rapid binary population synthesis code, which is freely available at \url{http://github.com/TeamCOMPAS/COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}. The simulations performed in this work were simulated with a COMPAS version that predates the publicly available code. Our version of the code is most similar to version 02.13.01 of the publicly available COMPAS code. Requests for the original code can be made to Floor Broekgaarden. The authors used {\sc{STROOPWAFEL}} from \citep{Broekgaarden+2019}, publicly available at \url{https://github.com/FloorBroekgaarden/STROOPWAFEL}\footnote{For the latest pip installable version of STROOPWAFEL please contact Floor Broekgaarden.}.
The authors also made use of Python from the Python Software Foundation. Python Language Reference, version 3.6. Available at \url{http://www.python.org}. In addition the following Python packages were used: matplotlib (\url{https://matplotlib.org/}), {NumPy} (\url{https://numpy.org/}), SciPy (\url{https://www.scipy.org/}), Jupyter Lab (\url{https://jupyter.org/}), seaborn (\url{https://seaborn.pydata.org/}), h5py (https://www.h5py.org/) and Astropy (\url{http://www.astropy.org}).  This research has made use of NASA’s Astrophysics Data System Bibliographic Services. We also made use of the computational facilities from the Harvard FAS Research Computing cluster.}
